Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-06 paper_jasa.tex
Poisson Binomial reference
lead into lemma 3.1

\hh{If there is evidence for individual skills influencing the probability $p_i$, then $X_i \sim Binom_{1, p+i}$ and $X$ is a sum of independent Bernoulli random variables with different success rates $p_i$. This makes the distribution of $X$ a Poisson-Binomial by definition, see XXX for details. estimating $p_i$ will be one of the main concerns for the remainder of the paper.}

@@

We need to make two crucial assumptions:
\begin{enumerate}
\item  the plot setup is structured in a way that makes it possible for observer to identify a deviation from the null hypothesis,
\item an observer is able to identify the plot with the strongest `signal' (or deviation from $H_0$)  from a lineup.
\end{enumerate}
We will be able to show evidence for the second assumption with the help of the study discussed in section~\ref{sec:simulation}, the first assumption well be reflected by the power of a lineup. The better suited a design is for a particular task, the higher its power will be.

>>>>

\hh{If there is evidence for individual skills influencing the probability $p_i$, then $X_i \sim Binom_{1, p+i}$ and $X$ is a sum of independent Bernoulli random variables with different success rates $p_i$. This makes the distribution of $X$ a Poisson-Binomial by definition, see \citet{butler93} for details. estimating $p_i$ will be one of the main concerns for the remainder of the paper.}

@@

We need to make two crucial assumptions:
\begin{enumerate}
\item  the plot setup is structured in a way that makes it possible for observer to identify a deviation from the null hypothesis,
\item an observer is able to identify the plot with the strongest `signal' (or deviation from $H_0$)  from a lineup.
\end{enumerate}
We will be able to show evidence for the second assumption with the help of the study discussed in section~\ref{sec:simulation}, \hh{the degree to which the first assumption is fulfilled is reflected} by the power of a lineup. The better suited a design is for a particular task, the higher its power will be.

\hh{In order to compare power of classical tests and lineups side-by-side, we will have to assume, that we are in the controlled environment of a simulation with tests corresponding to a known parameter value $\theta \in R$ and associated distribution function $F_t$ of the test statistic. }
